---
title: "Stormwater Occupancy Models"
author: "Alan Ivory"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---
## Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(readxl,questionr, parameters, ggplot2, ggthemes, tidyr, dplyr, reshape2, unmarked, gtable, grid, gridExtra, jpeg, lubridate, tibble, magrittr, MuMIn)

rm(list=ls()) 


observations <- read_excel("StormFindingsT_UE.xlsx")

```

## Data Wrangling

# Format data weekly

```{r DataWeek}
observations_weekly <- observations %>%
  group_by(OID, week = format(as.Date(Date), "%Y-%U"), Species) %>%
  summarise(observations = n()) %>%
  ungroup()

observations_species <- observations_weekly %>%
  pivot_wider(names_from = Species, values_from = observations)
```

# Focal Species

```{r FocSpecies, echo=FALSE}
focal_sp='Procyon_lotor'

observations_species_filled <- observations_species %>%
  mutate(across(all_of(focal_sp), ~ replace_na(.x, 0)))

```

# Occupancy Table

```{r OccupancyTable}
y_dat <- observations_species_filled[,c("OID", "week", focal_sp)] %>% # Subset to just raccoons
  pivot_wider(names_from = week , values_from = focal_sp) # Shift to wide format

y_mat <- as.matrix(y_dat[,unique(observations_species_filled$week)])

row.names(y_mat) <- y_dat$OID

y_mat[y_mat>1 & is.na(y_mat)==F] <- 1

```

# Import Effort Matrix and Location Data

```{r EffLoc}
loc <- read_excel("locT_UE.xlsx")
Eff_Mat <- read_excel("Eff_Mat_UE.xlsx")

table(loc$OID == row.names(y_mat))

```

# Standardizing covariates

```{r Standardize}
z_locs <- stdize(loc)

```

# Build Unmarked Frame

```{r UnmarkedOccu}
un_dat <- unmarkedFrameOccu(y = y_mat, # occupancy data
                            siteCovs = z_locs) # site covariates 
```

# General Model

```{r GenModel}
m0 <- occu(formula = ~1 # detection formula first
           ~1, # occupancy formula second,
           data = un_dat)

summary(m0)


backTransform(m0, type = "state")

backTransform(m0, type = "det")

```

# Model Building

```{r ModelBuild}

# Fit general model all variables
m0 <- occu(formula = ~1 # detection formula first
           ~1, # occupancy formula second,
           data = un_dat)


####This is the only one I have worked with as of 7/11/2023
# Occupancy is influence by System Size####
m1 <- occu(formula = ~1 # detection formula first
           ~z.System.Size, # occupancy formula second,
           data = un_dat)

# Occupancy is influence by Traffic
#m2 <- occu(formula = ~1 # detection formula first
          # ~z.Speed.Limit, # occupancy formula second,
          # data = un_dat)

#This is the second one I have worked with as of 7/11/2023
# Occupancy is influence by Distance to exit
m3 <- occu(formula = ~1 # detection formula first
           ~z.Distance.to.Exit, # occupancy formula second,
           data = un_dat)

# Occupancy is influence by Pipes within 100M
m4 <- occu(formula = ~1 # detection formula first
           ~z.Pipe.within.100M, # occupancy formula second,
           data = un_dat)


#This is the third one I have worked with as of 7/11/2023
# Occupancy is influence by Distance to Pond
m5 <- occu(formula = ~1 # detection formula first
           ~z.Pipe.Size, # occupancy formula second,
           data = un_dat)


# Occupancy is influence by Number of Nodes
m6 <- occu(formula = ~1 # detection formula first
           ~z.Nodes, # occupancy formula second,
           data = un_dat)

# Occupancy is influence by Number of Nodes
m7 <- occu(formula = ~1 # detection formula first
           ~z.Cross.Road, # occupancy formula second,
           data = un_dat)

# Occupancy is influence by Nearest Road Size
m8 <- occu(formula = ~1 # detection formula first
           ~z.Nearest.Road.Size, # occupancy formula second,
           data = un_dat)

# Occupancy is influence by Distance from Light
m9 <- occu(formula = ~1 # detection formula first
           ~z.Depth, # occupancy formula second,
           data = un_dat)

# Occupancy is influence by Distance to exit
#m10 <- occu(formula = ~1 # detection formula first
      #      ~z.Distance.to.Pond, # occupancy formula second,
       #     data = un_dat)


# Occupancy is influence by Impervious Surface percentage
m11 <- occu(formula = ~1 # detection formula first
            ~z.Imp_NLCD, # occupancy formula second,
            data = un_dat)

# Occupancy is influence by Impervious Surface percentage and Speed Limit
#m12 <- occu(formula = ~1 # detection formula first
          #  ~z.Impervious.Percentage + z.Speed.Limit, # occupancy formula second,
         #   data = un_dat)

# Occupancy is influence by Distance to an exit and Distance to a Pond
#m13 <- occu(formula = ~1 # detection formula first
      #      ~z.Distance.to.Exit + z.Distance.to.Pond, # occupancy formula second,
     #       data = un_dat)

# Occupancy is influence by Distance to an exit and SSS Pipe Size
m14 <- occu(formula = ~1 # detection formula first
            ~z.Distance.to.Exit + z.Pipe.Size, # occupancy formula second,
            data = un_dat)

# Occupancy is influence by Impervious Surface percentage and SSS System Size
m15 <- occu(formula = ~1 # detection formula first
            ~z.Imp_NLCD + z.System.Size, # occupancy formula second,
            data = un_dat)

# Occupancy is influence by Distance to an exit and Nearest Road Size
m16 <- occu(formula = ~1 # detection formula first
            ~z.Distance.to.Exit + z.Nearest.Road.Size, # occupancy formula second,
            data = un_dat)

# Occupancy is influence by Distance to an exit and Speed Limit
#m17 <- occu(formula = ~1 # detection formula first
     #       ~z.Distance.to.Exit + z.Speed.Limit, # occupancy formula second,
     #       data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by System Size####
m18 <- occu(formula = ~z.Depth # detection formula first
           ~z.System.Size, # occupancy formula second,
           data = un_dat)
# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by Speed Limit####
#m19 <- occu(formula = ~z.Depth # detection formula first
      #      ~z.Speed.Limit, # occupancy formula second,
      #      data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by System Size####
m20 <- occu(formula = ~z.Depth # detection formula first
           ~z.Distance.to.Exit, # occupancy formula second,
           data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by Pipe Avalibility within 100M####
m21 <- occu(formula = ~z.Depth # detection formula first
            ~z.Pipe.within.100M, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by Pipe size####
m22 <- occu(formula = ~z.Depth # detection formula first
            ~z.Pipe.Size, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by Number of pipe nodes at camera site####
m23 <- occu(formula = ~z.Depth # detection formula first
            ~z.Nodes, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by if the pipe crosses the road####
m24 <- occu(formula = ~z.Depth # detection formula first
            ~z.Cross.Road, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by Nearest Road Size####
m25 <- occu(formula = ~z.Depth # detection formula first
            ~z.Nearest.Road.Size, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the distance from the camera to the ground####
m26 <- occu(formula = ~z.Depth # detection formula first
            ~z.Depth, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by Distance to pond####
#m27 <- occu(formula = ~z.Depth # detection formula first
        #    ~z.Distance.to.Pond, # occupancy formula second,
         #   data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by Impervious Surface percentage####
m28 <- occu(formula = ~z.Depth # detection formula first
            ~z.Imp_NLCD, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by Impervious Surface percentage and Speed Limit
#m29 <- occu(formula = ~z.Depth # detection formula first
       #     ~z.Impervious.Percentage + z.Speed.Limit, # occupancy formula second,
       #     data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the distance to an exit and the distance to a pond
#m30 <- occu(formula = ~z.Depth # detection formula first
 #           ~z.Distance.to.Exit + z.Distance.to.Pond, # occupancy formula second,
  #          data = un_dat)


# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the distance to an exit and the pipe size
m31 <- occu(formula = ~z.Depth # detection formula first
            ~z.Distance.to.Exit + z.Pipe.Size, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by Impervious Surface percentage and System size
m32 <- occu(formula = ~z.Depth # detection formula first
            ~z.Imp_NLCD + z.System.Size, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the distance to an exit and the nearest road size
m33 <- occu(formula = ~z.Depth # detection formula first
            ~z.Distance.to.Exit + z.Nearest.Road.Size, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the distance to an exit and the speed limit
#m34 <- occu(formula = ~z.Depth # detection formula first
     #       ~z.Distance.to.Exit + z.Speed.Limit, # occupancy formula second,
     #       data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by if the systems crosses a road and the nearest road size
m35 <- occu(formula = ~z.Depth # detection formula first
            ~z.Cross.Road + z.Nearest.Road.Size, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the impervious percentage and the pipe size
m36 <- occu(formula = ~z.Depth # detection formula first
            ~z.Imp_NLCD + z.Pipe.Size, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the system size and the depth
m37 <- occu(formula = ~z.Depth # detection formula first
            ~z.System.Size + z.Depth, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the distance to an exit and the nodes
m38 <- occu(formula = ~z.Depth # detection formula first
            ~z.Distance.to.Exit + z.Nodes, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the pipe avalibility and nodes
m39 <- occu(formula = ~z.Depth # detection formula first
            ~z.Pipe.within.100M + z.Nodes, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the distance to an exit and the system size
m40 <- occu(formula = ~z.Depth # detection formula first
            ~z.Distance.to.Exit + z.System.Size, # occupancy formula second,
            data = un_dat)
# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by if the systems crosses a road and the nearest road size
m41 <- occu(formula = ~1 # detection formula first
            ~z.Cross.Road + z.Nearest.Road.Size, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the impervious percentage and the pipe size
m42 <- occu(formula = ~1 # detection formula first
            ~z.Imp_NLCD + z.Pipe.Size, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the system size and the depth
m43 <- occu(formula = ~1 # detection formula first
            ~z.System.Size + z.Depth, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the distance to an exit and the nodes
m44 <- occu(formula = ~1 # detection formula first
            ~z.Distance.to.Exit + z.Nodes, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the pipe avalibility and nodes
m45 <- occu(formula = ~1 # detection formula first
            ~z.Pipe.within.100M + z.Nodes, # occupancy formula second,
            data = un_dat)

# Detection is influenced by the distance from the camera to the ground, Occupancy is influence by the distance to an exit and the system size
m46 <- occu(formula = ~1 # detection formula first
            ~z.Distance.to.Exit + z.System.Size, # occupancy formula second,
            data = un_dat)
```

# Model Selection

```{r ModelSelect, echo=TRUE}
model.sel(m0,m1,m3,m4,m5,m6,m7,m8,m9,m11,m14,m15,m16,m18,
          m20,m21,m22,m23,m24,m25,m26,m28,m31,m32,m33,m35,m36,m37,m38,m39,m40,m41,m42,m43,m44,m45,m46)

#Model Selector without additive covariants
#model.sel(m0,m1,m3,m4,m5,m6,m7,m8,m9,m11,m18,m20,m21,m22,m23,m24,m25,m26,m28)
```

# Summary of Best Model

```{r BestModel, echo=TRUE}
summary(m20)
summary(m33)
```

## Odds Ratios- Raccoon
```{r OddsRatios_raccoon1, echo=TRUE}
test = summary(m20)

vcov_matrix <- vcov(m20)

# Detection
# Calculate the odds ratio
odds_ratio <- exp(summary(m20)$det$Estimate[2]) # Insert log odds ratio
odds_ratio

# Calculate the SE of the odds ratio using the delta method
se_odds_ratio <- sqrt(odds_ratio^2 * diag(vcov_matrix))
se_odds_ratio

# Occupancy
# Calculate the odds ratio
odds_ratio <- exp(summary(m20)$state$Estimate[2]) # Insert log odds ratio
odds_ratio

# Calculate the SE of the odds ratio using the delta method
se_odds_ratio <- sqrt(odds_ratio^2 * diag(vcov_matrix))
se_odds_ratio
```

## Odds Ratios- Raccoon2
```{r OddsRatios_raccoon2, echo=TRUE}
test1 = summary(m33)
vcov_matrix <- vcov(m33)

# Detection
# Calculate the odds ratio
odds_ratio <- exp(summary(m33)$det$Estimate[2]) # Insert log odds ratio
odds_ratio

# Calculate the SE of the odds ratio using the delta method
se_odds_ratio <- sqrt(odds_ratio^2 * diag(vcov_matrix))
se_odds_ratio

# Occupancy- Distance to Exit
# Calculate the odds ratio
odds_ratio <- exp(summary(m33)$state$Estimate[2]) # Insert log odds ratio
odds_ratio

# Calculate the SE of the odds ratio using the delta method
se_odds_ratio <- sqrt(odds_ratio^2 * diag(vcov_matrix))
se_odds_ratio

# Occupancy- Nearest Road Size
# Calculate the odds ratio
odds_ratio <- exp(summary(m33)$state$Estimate[3]) # Insert log odds ratio
odds_ratio

# Calculate the SE of the odds ratio using the delta method
se_odds_ratio <- sqrt(odds_ratio^2 * diag(vcov_matrix))
se_odds_ratio
```

### Distance to Exit Occupancy Model

```{r BestMod_Dist, echo=TRUE}

# Generate new data to predict from 
new_dat <- cbind(expand.grid(
  z.Distance.to.Exit=seq(min(z_locs$z.Distance.to.Exit),max(z_locs$z.Distance.to.Exit), 
                         length.out=25)))

# Make the predicted values                
new_dat <- predict(m20, type="state", newdata = new_dat, appendData=TRUE)


P1 <- ggplot(new_dat, aes(x = z.Distance.to.Exit, y = Predicted)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, linetype = "dashed") + # Confidence intervals
  geom_path(size = 1, color = "orange") +  # Set line color to orange
  labs(x = "Distance to Exit", y = "Occupancy Probability") + # axis labels
  theme_classic() +
  coord_cartesian(ylim = c(0, 1)) +
  theme(
    text = element_text(size = 16)  
  )

P1

```

### Set up for Additive Model with Distance to Exit and Nearest Road Size

```{r SetUp_BestMod_DistLanes, echo=TRUE}

#just looking at the model output
summary(m33)
nd = data.frame()


nd_0 = data.frame(z.Distance.to.Exit=seq(min(scale(loc$Distance.to.Exit)),max(scale(loc$Distance.to.Exit)),length=100),
                     z.Nearest.Road.Size=rep(0,100))
nd_0_predict = predict(m33,type="state",newdata=nd_0,appendData=TRUE)

nd_1 = data.frame(z.Distance.to.Exit=seq(min(scale(loc$Distance.to.Exit)),max(scale(loc$Distance.to.Exit)),length=100),
                  z.Nearest.Road.Size=rep(1,100))
nd_1_predict = predict(m33,type="state",newdata=nd_1,appendData=TRUE)

nd_2 = data.frame(z.Distance.to.Exit=seq(min(scale(loc$Distance.to.Exit)),max(scale(loc$Distance.to.Exit)),length=100),
                  z.Nearest.Road.Size=rep(2,100))
nd_2_predict = predict(m33,type="state",newdata=nd_2,appendData=TRUE)

nd_3 = data.frame(z.Distance.to.Exit=seq(min(scale(loc$Distance.to.Exit)),max(scale(loc$Distance.to.Exit)),length=100),
                  z.Nearest.Road.Size=rep(3,100))
nd_3_predict = predict(m33,type="state",newdata=nd_3,appendData=TRUE)

nd_4 = data.frame(z.Distance.to.Exit=seq(min(scale(loc$Distance.to.Exit)),max(scale(loc$Distance.to.Exit)),length=100),
                  z.Nearest.Road.Size=rep(4,100))
nd_4_predict = predict(m33,type="state",newdata=nd_4,appendData=TRUE)

nd_5 = data.frame(z.Distance.to.Exit=seq(min(scale(loc$Distance.to.Exit)),max(scale(loc$Distance.to.Exit)),length=100),
                  z.Nearest.Road.Size=rep(5,100))
nd_5_predict = predict(m33,type="state",newdata=nd_5,appendData=TRUE)

nd_all <- data.frame(z.Distance.to.Exit = rep(seq(min(scale(loc$Distance.to.Exit)),max(scale(loc$Distance.to.Exit)),length=100),6), 
                     z.Nearest.Road.Size = c(rep(0,100),rep(1,100),rep(2,100),rep(3,100),rep(4,100),rep(5,100)),
                     Predicted =c(nd_0_predict$Predicted,nd_1_predict$Predicted,nd_2_predict$Predicted,
                                  nd_3_predict$Predicted,nd_4_predict$Predicted,nd_5_predict$Predicted),
                     lower = c(nd_0_predict$lower,nd_1_predict$lower,nd_2_predict$lower,
                               nd_3_predict$lower,nd_4_predict$lower,nd_5_predict$lower),
                     upper=c(nd_0_predict$upper,nd_1_predict$upper,nd_2_predict$upper,
                             nd_3_predict$upper,nd_4_predict$upper,nd_5_predict$upper))

```

### Distance to Exit and Nearest Road Size Occupancy Model

```{r BestMod_DistLanes, echo=TRUE}

P2 = ggplot(nd_all,x=z.Distance.to.Exit,y=Predicted)+
  geom_ribbon(data=nd_0_predict, aes(x=z.Distance.to.Exit,ymin=lower,ymax=upper),inherit.aes = FALSE,fill = "gray",alpha=0.1)+
  geom_ribbon(data=nd_1_predict, aes(x=z.Distance.to.Exit,ymin=lower,ymax=upper),inherit.aes = FALSE,fill = "gray",alpha=0.1)+
  geom_ribbon(data=nd_2_predict, aes(x=z.Distance.to.Exit,ymin=lower,ymax=upper),inherit.aes = FALSE,fill = "gray",alpha=0.1)+
  geom_ribbon(data=nd_3_predict, aes(x=z.Distance.to.Exit,ymin=lower,ymax=upper),inherit.aes = FALSE,fill = "gray",alpha=0.1)+
  geom_ribbon(data=nd_4_predict, aes(x=z.Distance.to.Exit,ymin=lower,ymax=upper),inherit.aes = FALSE,fill = "gray",alpha=0.1)+
  geom_ribbon(data=nd_5_predict, aes(x=z.Distance.to.Exit,ymin=lower,ymax=upper),inherit.aes = FALSE,fill = "gray",alpha=0.1)+
  geom_line(data=nd_0_predict,aes(x=z.Distance.to.Exit,y=Predicted,color="blue"))+
  geom_line(data=nd_1_predict,aes(x=z.Distance.to.Exit,y=Predicted,color="orange"))+
  geom_line(data=nd_2_predict,aes(x=z.Distance.to.Exit,y=Predicted,color="green"))+
  geom_line(data=nd_3_predict,aes(x=z.Distance.to.Exit,y=Predicted,color="purple"))+
  geom_line(data=nd_4_predict,aes(x=z.Distance.to.Exit,y=Predicted,color="magenta"))+
  geom_line(data=nd_5_predict,aes(x=z.Distance.to.Exit,y=Predicted,color="black"))+
  theme_bw()+xlab("Distance to Exit")+ylab("Occupancy Probability")+
  theme(legend.position="top", text = element_text(size = 16)) +
  scale_color_manual(values=c("blue","orange","green","purple","magenta","black"),
                     labels=c("0 lanes","1 lane","2 lanes","3 lanes","4 lanes","5 lanes"))+
  labs(color="Number of Lanes of Traffic")



# legend
P2 + scale_color_manual(
  values = c("blue", "orange", "green", "purple", "magenta", "black"),
  labels = c("0 lanes", "1 lane", "2 lanes", "3 lanes", "4 lanes", "5 lanes")
) +
  labs(color = "Number of Lanes of Traffic")

```

## Figure Grid
```{r FigureGrid, echo=TRUE}
final_plot <- (P1 + P2) +
  plot_annotation(tag_levels = 'a') +
  plot_layout(widths = c(1, 1), heights = c(1)) & 
  theme_classic() &
  theme(legend.position="top")


# Print the combined plot
final_plot

agg_png(file = "final_plot_bat.png", width = 10, height = 3, units = "in", res = 600, scaling = 0.6)
final_plot
dev.off()
```
